Dependent Object Types

### 2012-08-05 article.tex
revised dot-two

The expansion relation $\expand$ is needed to typecheck the complete
set of declarations carried by a concrete type that is used in a
\textbf{new}-expression.  Since this is the only place where expansion
is needed, it is sufficient to define it on concrete types only. The
bottom part of Figure~\ref{dot-two} gives the typing rules for
expansion.

Rule (\textsc{rfn-$\expand$}) states that a refinement type $T_c
\expand_z {\seq D}$ expands to the conjunction of the expansion $D'$
of $T_c$ and the newly added declarations $D$. Rule
(\textsc{tsel-$\expand$}) states that a type selection $p.L$ carries
the same declarations as the upper bound $U$ of $L$ in $T$.  Rule
($\tand$-$\expand$) states that expansion distributes through meets.
Rule (\textsc{$\top$-$\expand$}) states that the top type $\top$
expands to the empty set.

>>>>

The expansion relation $\expand$ is needed to typecheck the complete
set of declarations carried by a concrete type that is used in a
\textbf{new}-expression. Expansion is also used in subtyping
refinements on the right (see \figref{dot-sub}).

Rule (\textsc{rfn-$\expand$}) states that a refinement type $T
\expand_z {\seq D}$ expands to the conjunction of the expansion $D'$
of $T$ and the newly added declarations $D$. Rule
(\textsc{tsel-$\expand$}) states that a type selection $p.L$ carries
the same declarations as the upper bound $U$ of $L$ in $T$.  Rules
($\tand$-$\expand$) and ($\tor$-$\expand$) states that expansion
distributes through meets and joins.  Rule (\textsc{$\top$-$\expand$})
states that the top type $\top$ expands to the empty set. Rule
(\textsc{$\bot$-$\expand$}) states that the bottom type $\bot$ expands
to the bottom element $\seq{D_\Bot}$ of the lattice of sets of
declarations (recall \figref{dot-decls}).
